---
title: "STAT 625 Week 1 (a single class)"
author: "Jay Emerson and Susan Wang"
date: "September 1, 2016"
output: pdf_document
---

## Computing and Reproducible Research

This document was produced in R Studio using R Markdown, choosing
the PDF option for the document.  You can work without R Studio, but
R Studio makes many things like this wonderfully easy.
And R Markdown itself is pretty simple (far simpler
than full-blown \LaTeX).  You'll need packages `knitr` and
`rmarkdown`.  You'll also want \LaTeX\ on your system,
though you won't use it directly.  In Windows, this is called
`MiKTeX`.  The full, complete distribution is required (and is
quite large, about 2 GB -- don't try to download it during class,
please).  The `MiKTeX` installer will really try to encourage you to
install the basic version.  It won't work.  Trust us, keep your
eyes open.  On the Mac, you'll need `MacTeX`.  It's an easy
installation.  Anyone using Linux?  Probably not, but if so it's likely
you can be self-sufficient.

Recommendation: start by installing R (www.r-project.org) and
either `MiKTeX` or `MacTeX`.  Then install R Studio.  We had 110
students last semester, and only 2 problems.  These problems
arose when something wasn't quite right and (for example), the
student tried to recover by modifying the registry in Windows.
Don't do crazy stuff like that.


## HINT

Work together on computing stuff like this!  There are lots of little
computing "gotchas" that can
be annoying, but fighting through them and succeeding is important.  When
you graduate and get a real job (or head to graduate school or whatever),
being able to solve problems and be computationally self-sufficient will
be valuable.  Yes, we're here to study statistics (or data analysis,
we would prefer to say).  But we aren't here just to
___think about___ problems; we're
here to ___work on___ problems.  Thinking is necessary, but not sufficient.

## Markdown?

Looking for information about Markdown? 
Try http://daringfireball.net/projects/markdown/.

## LaTeX?

Let's call this essential if you are doing a PhD -- you'll use it
for your dissertation and for 95\% of the papers you write.  But for
many it is probably overkill and R Markdown and R scripts will be
sufficient.  As a side note, you can include many \LaTeX\ things in
R Markdown documents.

## Toy Example

Let's try a data set that Jay has available on the web.  This is
a code chunk, which is processed and nicely displayed with the output
in the resulting PDF:
```{r}
x <- read.csv("http://www.stat.yale.edu/~jay/diving/Diving2000.csv",
              as.is=TRUE)
dim(x)
mean(x$JScore)
```
And R Markdown also makes it easy to integrate graphics.  Note that only
one graphical display should appear in any one code chunk.
```{r}
hist(x$JScore, xlab="Score",
     main="Distribution of Judges' Scores",
     breaks=seq(-0.25, 10.25, by=0.5))
```

## Reproducible?

This document is entirely ___reproducible___ as long as you have the original
R Markdown file, `Y16_W1.Rmd`. You should be able to reproduce this document
exactly (or with perhaps superficial formatting differences), including the
amazing analysis and plot.  Using
\LaTeX\ involves a similar workflow that includes code with the
document, but is (potentially) more complicated (and hence potentially
much more sophisticated).  With every passing month I find myself preferring
R Markdown.

## In this course...

We won't micromanage your computing environment as long as we like the
results.  We'll pick on you mercilessly for bad code (while trying to maintain
a sense of humor about it early in the term).  Bad code leads
to mistakes and wasted time.  We don't like either.  And of course
we value communication... so effectively, neatly, and concisely
presenting your work will be an important component of the course.

## TODAY

- Syllabus
- Hoops data scrape example
- Basic New Haven real estate property record toy scrape and challenge
- Homework for Tuesday (yes really)


## Homework Due Tuesday 9/6

We will provide the VisionAppraisal files (to be briefly visible and
unprotected shortly in Jay's `www.stat.yale.edu/~jay/625/` folder). 
Please use this version.
That is, please don't scrape them directly
from the web site -- it generates lots of traffic (more than 1.5 GB per batch)
and may cause problems.

Create a data frame with three columns (and 27307 rows, because 27307 is the
maximum observed parcel id we seem to have this year):
parcel id (call it `pid`),
raw address (call it `location`), and the 2015 total appraised value
(call it `totval`).  You'll have a row for each property -- if there is
no information (or no raw file) there should still be a row for it in the
data set (with the `pid` but `NA` values for the other variables).
Example: for parcel number 600, the `pid` would be 600,
the `location` would be "108 HYDE ST", and the `totval` would
be the number 235600 (not the text "\$235,600").

Save this data frame as a CSV file "hw1.csv" that __does not have row names__.
Upload it to your dropbox on ClassesV2, along with your script that did the
work.  The comments at the top of the script should acknowledge any
collaboration (working together is fine but your script should be your own
work and you should understand everything that you do).  Intentation and
quality of code matters.  See the `R_Code_Guidelines.R`, which we're happy
to add to.
